---
title: "Assignment 1"
author: "Cem Deniz SAYINER"
date: "2024-01-09"
---

## 1.Introduce yourself in one paragraph (Your name surname, your work, your data interests and how you (plan to) use data science skills in your current/future work). Add your Linkedin account link.

### About me

Cem Deniz SAYINER, I have been working as a Senior R&D Engineer at ISBAK for 3 years. I possess 8 years of experience in software development, with the last 3 years focused on developing software for AI-Based Video Analytics Systems. I am enthusiastic about utilizing cutting-edge technology and open to new experiences in different fields that will help me expand my horizons.

[To visit my LinkedIn Account](https://www.linkedin.com/in/cem-deniz-s-7511911a8)

## 2. Watch some demo and tutorial videos from [Posit Youtube channel playlist](https://youtube.com/playlist?list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&si=o2Vh9XiQT_pnMo_B) and write one of them down on your Quarto document.

### **What is data wrangling? Intro, Motivation, Outline, Setup \-- Pt. 1 Data Wrangling Introduction**

[Tutorial Videos Link](https://www.youtube.com/watch?v=jOd65mR1zfw&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=208)

```{r}
library(dplyr)
library(ggplot2)

diamonds
```

```{r}

as_tibble(diamonds)


```

```{r}
View(diamonds)
```

```{r}
diamonds$x %>%
  round(2)  %>%
  mean()
```

Alternatively :

```{r}
d2 <- round(diamonds$x,2)
mean(d2)
```
